\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2019

% ready for submission
% \usepackage{neurips_2019}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
\usepackage[preprint]{neurips_2019}

% to compile a camera-ready version, add the [final] option, e.g.:
%\usepackage{neurips_2019}

% to avoid loading the natbib package, add option nonatbib:
%     \usepackage[nonatbib]{neurips_2019}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{array}
\newcolumntype{L}{>{\centering\arraybackslash}m{7.5cm}}
% for importing images
\usepackage{graphicx}
\graphicspath{
	{graphics/}
}

\usepackage{pythonhighlight}

\title{Mimic: Character Based Chatbot}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
	Nirvan S P Theethira\\
	%  Department of Computer Science\\
	%  University of Colorado Boulder\\
	\texttt{nith5605@colorado.edu} \\
	\And
	Charlie Carlson\\
	%  Department of Computer Science\\
	%  University of Colorado Boulder\\
	\texttt{chca0914@colorado.edu} \\
	\And
	Ketan Ramesh\\
	\texttt{kerk1228@colorado.edu} \\
	\And
	Pramod Venkatesh Kulkarni\\
	%  Department of Computer Science\\
	%  University of Colorado Boulder\\
	\texttt{prku8035@colorado.edu} \\
}

\begin{document}
	
	\maketitle
	
	\begin{abstract}
		In this project we explored the problem of creating a chatbot that could mimic a popular television character's personality, Joey from Friends.
		Our dataset was extracted directly from the Friends scripts from each season. 
		We worked with two different neural network models which we trained on the same dataset: a sequence-to-sequence model and a transformer model. 
		To evaluate our models' performance we considered automatic metrics often used to evaluate translation bots and a human based metric inspired by the Turing test.
		Not surprisingly, neither model performed well with respect to the automatic metrics.
		Moreover, we found that both models failed to consistently convince a human tester that their responses captured the personality of Joey.
		We review a collection of troublesome instances for each model and theorize ways in which each model could be improved.
		We conclude that both models had only minor success but it may be interesting to experiment with slightly more complex models and different datasets. 
	\end{abstract}
	
	\section{Introduction}
	\input{intro.tex}

	\section{Dataset and Evaluation}
	In this section we review what datasets we used, how we created them and how we evaluated the performance of our models on them.
	\input{data.tex}
	\input{eval.tex}
	
	\section{The Sequence-to-Sequence Model}
	\input{mimic.tex}
	\section{Transformer Model}
	
	\input{mimic_transform.tex}
	
	\section{Conclusion}
	\input{conclusion}
	\subsubsection*{Acknowledgments}
	
	We would like to thank Chenhao Tan, Brian Groenke, Aakarsh Fadnis, and Madhusudhan Aithai Mahabhaleswhwara for their feedback on this project.
	
	\bibliography{references}
	\bibliographystyle{unsrt}
	
\end{document}